---
title: "eds221-comp10"
format: html
editor: visual
---

## 

```{r}
library(tidyverse)
library(here)
library(janitor)
```

```{r}
madison_ice <- read_csv(here("data", "ntl33_v7.csv"))
madison_meteor <- read_csv(here("data", "ntl20_v6.csv"))
```

Create a visualization that compares ice duration across
different lakes in the Madison Lake Area. Include both the actual ice
duration values *and* some representation of summary statistics
for each lake. Careful if you use a boxplot over a jitter or beeswarm -
what values might be doubly represented? Can you find an argument that
would help you remove those from the boxplot?

```{r}
madison_ice %>% 
  drop_na(ice_duration) %>% 
ggplot(aes(x = lakeid, y = ice_duration)) +
  geom_jitter() 
```

Find the mean ice cover duration in Madison Lake Area by year
(i.e., you\'ll only be grouping by the year variable here). Understanding
check: what are you finding the mean of here? Why are there multiple
observations for each year?)

```{r}
mean_ice <- madison_ice %>% 
  group_by(year4) %>% 
  summarise(mean_by_year = mean(iceon, na.rm = TRUE))
```

Create an exploratory visualization of mean ice cover duration by
year for the Madison Lake Area. Add a sentence or two below this
exploratory graph describing the overall trend(s) you observe.

```{r}
mean_ice %>% 
  drop_na(year4, mean_by_year) %>% 
ggplot(aes(x = year4, y = mean_by_year)) +
  geom_jitter()
```

Find the mean air temperature (using the daily average air
temperature - adjusted) in Madison Lake Area **by year**
using **only observations from winter months (December, January,
February)**

```{r}
mean_airtemp <- madison_meteor %>% 
  group_by(year4) %>% 
  filter(month %in% c(12, 1, 2)) %>% 
  summarise(mean_airadj = mean(ave_air_temp_adjusted, na.rm = "TRUE"))
```

Create an exploratory visualization of mean winter temperatures
for the Madison Lake Area. Add a sentence or two below this exploratory
graph describing the overall trend(s) you observe.

```{r}
ggplot(data = mean_airtemp, aes(x = month, y = "mean_airadj")) +
  geom_jitter()
```
